TacticToe: Learning to Prove with Tactics

### 2018-03-21 tactictoe_jv.tex
typo
minor

%A recent improvement on this system~\cite{}\todo{Cezary: could not remember
%the
%reference that you gave me here i think it was CICM 2017} includes the
%possibility to
%substitute theorems appearing in tactics by ones belonging to the same
%cluster.
%In this work, we are also able to predict theorems appearing as arguments of
%tactics but we rely only on information from the current goal. Combining the
%two approaches by predicting from the goal and from the original tactic
%arguments is more difficult but is likely to produce more suitable lemmas.
%
Proof Patching \cite{RingerYLG18} is an approach that attempts to learn the
proof changes necessary for a modification of a prover library or system. The
approach is hard to apply for new proofs. On the other had, \tactictoe could also
try to learn from different versions of the prover library.

>>>>

%A recent improvement on this system~\cite{}\todo{Cezary: could not remember
%the
%reference that you gave me here i think it was CICM 2017} includes the
%possibility to
%substitute theorems appearing in tactics by ones belonging to the same
%cluster.
%In this work, we are also able to predict theorems appearing as arguments of
%tactics but we rely only on information from the current goal. Combining the
%two approaches by predicting from the goal and from the original tactic
%arguments is more difficult but is likely to produce more suitable lemmas.
%
Proof patching \cite{RingerYLG18} is an approach that attempts to learn the
proof changes necessary for a modification of a prover library or system. The
approach is hard to apply for new proofs. Following this idea, \tactictoe 
could also try to learn from different versions of the prover library.
